Derogations, Democratic Backsliding, and International Human Rights During the COVID-19 Pandemic

### 2024-11-26 README.qmd
Fix line breaks
ope it wasn't a hidden unicode thing, it was an unclear emoji alias
{emoji} was randomly choosing between a smiling and a non-smiling emoji each time it rendered the README
Add DOI badges

[Suparna Chaudhry](https://www.suparnachaudhry.com/) • Lewis and Clark College
[Audrey Comstock](https://audreylcomstock.weebly.com/) • Arizona State University
[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University

<!-- badges: start -->
<!-- badges: end -->

@@

## `r emoji_glue(":lemon::devil:")`: Note on "lemon lucifer" project name

>>>>

[Audrey Comstock](https://audreylcomstock.weebly.com/) • Arizona State University  
[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University  
[Suparna Chaudhry](https://www.suparnachaudhry.com/) • Lewis and Clark College

<!-- badges: start -->
[![Preprint](https://img.shields.io/badge/Preprint-10.31235%2Fosf.io%2Fg3z6n-blue)](https://doi.org/10.31235/osf.io/g3z6n) [![OSF DOI](https://img.shields.io/badge/OSF%20project-10.17605%2FOSF.IO%2FWXPRN-blue)](https://doi.org/10.17605/OSF.IO/WXPRN) [![Code DOI](https://img.shields.io/badge/Code-10.5281%2Fzenodo.14220206-blue)](https://doi.org/10.5281/zenodo.14220206)
<!-- badges: end -->

@@

## `r emoji_glue(":lemon::smiling_face_with_horns:")`: Note on "lemon lucifer" project name
